Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-20 prop_letter.tex
prop_letter.tex \newcommand{\coreBorn}{\mathrm{C}} Added...

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
\allowdisplaybreaks

@@

@@

To formalize the idea of finite precision measurement, we next introduce 
the notion of quantum IVPM~$\bar{\mu}$. The latter replaces 
the infinitely precise interval $[0,1]$ by a finite collection $\mathscr{I}$ of
intervals. Since the intervals $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$ 
should be included in $\mathscr{I}$, and arithmetic operations on intervals satisfy
\begin{subequations}\label{eq:interval-operations}
\begin{eqnarray}
 &  & \left[1,1\right]-\left[l,r\right]=\left[1-r,1-l\right], \textrm{ and}\\
 &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}] ,
\end{eqnarray}
\end{subequations}
$\bar{\mu}:\events\rightarrow\mathscr{I}$ is defined by the axioms:
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
\item $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
$P_{i}P_{j}=\delta_{ij}P_{i}$, we have 
\begin{equation}
\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{itemize}
condition that provides only a bound and not an equivalence as in
Eq.~\eqref{eq:QuantumProbability-Addition}. For example, if we consider
$\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $ and
$\bar{\mu}\left(P\right)=\left[l,r\right]$, we have, when $r-l=\ell>0$,
\[
\bar{\mu}(\mathbb{1})=\left[1,1\right]\subsetneq\left[1-\ell,1+\ell\right]=\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right).
\]

Formally, we can ask: what can we deduce about the state of a quantum
system given a quantum interval-valued probability measure, i.e.,
given observations done with finite resources. Since the probabilities
are intervals, it is intuitive to say a state~$\rho$ is consistent
with $\bar{\mu}$ on a projector~$P$ if 
\begin{equation}
\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)\textrm{ .}
\end{equation}

@@

In the case that the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
any quantum probability measure can be recast as an interval-valued
one. For $d\ge3$, the question reduces to Gleason's theorem which
states that for any quantum IVPM~$\bar{\mu}$, there is an unique
state can be consistent with $\bar{\mu}$ on every projector.

While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
IVPM, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
is another one corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}.
However, before dive into the Kochen-Specker theorem, it is better
to understand how to define expectation value of an observable with
quantum IVPMs.

@@

Quantum IVPMs turns into the classical IVPMs setup~\cite{JamisonLodwick2004}
when the space of events includes only mutually commuting sub-events,
where any subset of $\events$ is called a sub-event space if it satisfies
the follow conditions. 
\begin{itemize}
\item $\mathbb{0}\in\events'$. 
\item $\mathbb{1}\in\events'$. 
\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
For example, $\events_{0}=\left\{ \mathbb{0},\proj{\ps},\proj{\ms},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\end{equation}
If we identify $\proj{0}$ and $\proj{1}$ as the head and the tail
of a coin, respectively, then $\bar{\mu}_{2}$ represents experimenter
know nothing about a coin before she toss it.

@@

To understand the relation between IVPMs and states, it is instructive
to consider the 2-dimensional quantum probability measure~$\mu_{0}:\events\rightarrow[0,1]$
defined as follow:
\begin{equation}
\mu_{0}(P)=\begin{cases}
\mu_{\ket{\ps}}^{\mathrm{B}}(P) & \textrm{, if }P\in\events_{0}\textrm{ ;}\\
\mu_{\ket{0}}^{\mathrm{B}}(P) & \textrm{, otherwis.}
\end{cases}
\end{equation}
$\mu_{0}$ is not induced by the Born rule as a whole, but is consistent
with the Born rule on $\events_{0}$ and some other proper sub-event
spaces. The similar phenomena happens for IVPMs as well. Formally,
given a quantum IVPM~$\bar{\mu}$, the \emph{core} relative to a
sub-event space~$\events'\subseteq\events$ is\footnote{\yutsung{I changed the definition of core to embedding the Born rule.
While this change might make it easier to explain the core of quantum
IVPMs, should we explain the meaning of the Born rule for classical
probability measures? Check this definition in the classical setting,
like commuting observables or product states... etc.}}
\begin{equation}
\mathrm{core}\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events'.~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
\end{equation}
The core of an interval-valued probability measure is the set of states
it approximates. For example, $\mathrm{core}\left(\bar{\mu}_{1},\events'\right)$
contains every density matrix. The 2-dimensional measure~$\mu_{0}$
can be understood by core as well. Consider the IVPM~$\bar{\mu}_{0}=\iota_{\infty}\circ\mu_{0}$
whose cores are\begin{subequations}
\begin{eqnarray}
\mathrm{core}\left(\bar{\mu}_{0},\events_{0}\right) & = & \left\{ \proj{\ps}\right\} \textrm{ ,}\\
\mathrm{core}\left(\bar{\mu}_{0},\events_{1}\right) & = & \left\{ \proj{0}\right\} \textrm{ ,}\\
\mathrm{core}\left(\bar{\mu}_{0},\events\right) & = & \emptyset\textrm{ ,}
\end{eqnarray}
\end{subequations}where $\events_{1}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $.
That is, $\bar{\mu}_{0}$ approximates $\proj{\ps}$ if we are only
allowed to use $\events_{0}$ during the measurement, and approximates
$\proj{0}$ if $\events_{1}$ are the only allowed ones. Since $\bar{\mu}_{0}$
approximates different states on different sub-event space, it intuitively
approximates nothing if every projector is allowed.

@@

\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}]\label{thm:Shapley}For
every interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
if the following conditions are true.
\begin{itemize}
\item $\events'$ is commutative, i.e., $\bar{\mu}$ is classical.
\item $\bar{\mu}$ is convex, i.e., for all commuting $P_{0},P_{1}\in\events$,
$\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
\end{itemize}
Then, $\mathrm{core}\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}

@@

Let $\events_{1}$ be the minimal event space containing both $\proj{0}$
and $\proj{\ps}$. Because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
for any mixed state~$\rho\in\mathrm{core}\left(\bar{\mu},\events_{1}\right)$,
we have $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$.
Hence, $\rho$ is actually the pure state orthogonal to both $\ket{0}$
and $\ket{\ps}$. The only choice of $\rho$ is $\ket{2}$, and it
is easy to verify $\proj{2}$ is actually in $\mathrm{core}\left(\bar{\mu},\events_{1}\right)$.

Similarly, let $\events_{2}$ be the minimal event space containing
both $\proj{0}$ and $\proj{\ps'}$. We have $\mathrm{core}\left(\bar{\mu},\events_{2}\right)=\left\{ \proj{1}\right\} $.
Therefore, 
\begin{equation}
\mathrm{core}\left(\bar{\mu},\events\right)\subseteq\mathrm{core}\left(\bar{\mu},\events_{1}\right)\cap\mathrm{core}\left(\bar{\mu},\events_{2}\right)=\emptyset\textrm{ ,}
\end{equation}
and must be empty.\end{example}

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
\allowdisplaybreaks
\newcommand{\coreBorn}{\mathrm{C}}

@@

Furthermore, if we express the observable~$\mathbf{O}$ as its spectrum
decomposition~$\sum_{i=1}^{N}\lambda_{i}P_{i}$, the expectation
value of $\mathbf{O}$ is given by~\cite{544199,Jaeger2007}
\begin{equation}
\expval{\mathbf{O}}_{\rho}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
\end{equation}

@@

To formalize the idea of finite precision measurement, we next introduce
the notion of quantum IVPM~$\bar{\mu}$. The latter replaces the
infinitely precise interval $[0,1]$ by a finite collection $\mathscr{I}$
of intervals. Since the intervals $\imposs=\left[0,0\right]$ and
$\necess=\left[1,1\right]$ should be included in $\mathscr{I}$,
and arithmetic operations on intervals satisfy \begin{subequations}\label{eq:interval-operations}
\begin{eqnarray}
 &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]\textrm{ and}\\
 &  & x[l,r]=\begin{cases}
[xl,xr] & \textrm{for }x\ge0\textrm{ ;}\\{}
[xr,xl] & \textrm{for }x\le0\textrm{ .}
\end{cases}
\end{eqnarray}
\end{subequations} $\bar{\mu}:\events\rightarrow\mathscr{I}$ is
defined by the axioms: 
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
\item $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
$P_{i}P_{j}=\delta_{ij}P_{i}$, we have 
\begin{equation}
\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{itemize}
condition that provides only a bound and not an equivalence as in
Eq.~\eqref{eq:QuantumProbability-Addition}. For example, if we consider
$\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $ and
$\bar{\mu}\left(P\right)=\left[l,r\right]$, we have, when $r-l=\ell>0$,
\[
\bar{\mu}(\mathbb{1})=\left[1,1\right]\subsetneq\left[1-\ell,1+\ell\right]=\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right).
\]

Formally, we can ask: what can we deduce about the state of a quantum
system given a quantum interval-valued probability measure, i.e.,
given observations done with finite resources. Since the probabilities
are now intervals, it is intuitive to say a state~$\rho$ is consistent
with $\bar{\mu}$ on a projector~$P$ if 
\begin{equation}
\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)\textrm{ ,}
\end{equation}
and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.

@@

In the case that the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
any quantum probability measure can be recast as an interval-valued
one. For $d\ge3$, the question reduces to Gleason's theorem which
states that for any quantum IVPM~$\bar{\mu}$, there is an unique
state consistent with $\bar{\mu}$ on every projector.

While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
IVPM, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
is another one, and corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}.
However, before dive into the Kochen-Specker theorem, it is better
to understand how to define expectation value of an observable with
quantum IVPMs.

\paragraph{Expectation Values for Quantum IVPMs}

Consider a quantum IVPM~$\bar{\mu}$ such that $l:\events\rightarrow\left[0,1\right]$
and $r:\events\rightarrow\left[0,1\right]$ are the left-end and the
right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
This time, when we express the observable~$\mathbf{O}$ as its spectrum
decomposition~$\sum_{i=1}^{N^{-}}\lambda_{i}^{-}P_{i}^{-}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}P_{i}^{+}$,
we separate the positive and negative eigenvalues and order them from
the smallest to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\textrm{ .}
\end{equation}
Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta f\left(P_{i}^{s\prime}\right)=f\left(P_{i}^{s\prime}\right)-f\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $f\in\left\{ l,r\right\} $.
We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
with (\ref{eq:quantum-expectation}) to define the expectation value
of $\mathbf{O}$ with respect to $\bar{\mu}$ as
\begin{eqnarray}
\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta l\left(P_{i}^{+\prime}\right),\Delta r\left(P_{i}^{+\prime}\right)\right]\\
 &  & +\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta l\left(P_{i}^{-\prime}\right),\Delta r\left(P_{i}^{-\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
\end{eqnarray}
Let $\events'$ denote the set containing $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}$
and satisfies the following conditions.
\begin{itemize}
\item $\mathbb{0}\in\events'$. 
\item $\mathbb{1}\in\events'$. 
\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
Then, we have the following theorem.

\begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
and any observable~$\mathbf{O}$, if $\bar{\mu}$ is convex, then
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}\label{eq:quantum-interval-expectation-core}
\end{equation}
Conversely, if equation~(\ref{eq:quantum-interval-expectation-core})
holds for every observable, then $\bar{\mu}$ is convex.\end{thm}

@@

Quantum IVPMs turns into the classical IVPMs setup~\cite{JamisonLodwick2004}
when the space of events includes only mutually commuting sub-events,
where any subset of $\events$ is called a sub-event space if it satisfies
the follow conditions.

For example, $\events_{0}=\left\{ \mathbb{0},\proj{\ps},\proj{\ms},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\end{equation}
If we identify $\proj{0}$ and $\proj{1}$ as the head and the tail
of a coin, respectively, then $\bar{\mu}_{2}$ represents experimenter
know nothing about a coin before she toss it.

@@

To understand the relation between IVPMs and states, it is instructive
to consider the 2-dimensional quantum probability measure~$\mu_{0}:\events\rightarrow[0,1]$
defined as follow:
\begin{equation}
\mu_{0}(P)=\begin{cases}
\mu_{\ket{\ps}}^{\mathrm{B}}(P) & \textrm{, if }P\in\events_{0}\textrm{ ;}\\
\mu_{\ket{0}}^{\mathrm{B}}(P) & \textrm{, otherwis.}
\end{cases}
\end{equation}
$\mu_{0}$ is not induced by the Born rule as a whole, but is consistent
with the Born rule on $\events_{0}$ and some other proper sub-event
spaces. The similar phenomena happens for IVPMs as well. Formally,
given a quantum IVPM~$\bar{\mu}$, the \emph{core} relative to a
sub-event space~$\events'\subseteq\events$ is\footnote{\yutsung{I changed the definition of core to embedding the Born rule.
While this change might make it easier to explain the core of quantum
IVPMs, should we explain the meaning of the Born rule for classical
probability measures? Check this definition in the classical setting,
like commuting observables or product states... etc.}}
\begin{equation}
\coreBorn\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events'.~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
\end{equation}
The core of an interval-valued probability measure is the set of states
it approximates. For example, $\coreBorn\left(\bar{\mu}_{1},\events'\right)$
contains every density matrix. The 2-dimensional measure~$\mu_{0}$
can be understood by core as well. Consider the IVPM~$\bar{\mu}_{0}=\iota_{\infty}\circ\mu_{0}$
whose cores are\begin{subequations}
\begin{eqnarray}
\coreBorn\left(\bar{\mu}_{0},\events_{0}\right) & = & \left\{ \proj{\ps}\right\} \textrm{ ,}\\
\coreBorn\left(\bar{\mu}_{0},\events_{1}\right) & = & \left\{ \proj{0}\right\} \textrm{ ,}\\
\coreBorn\left(\bar{\mu}_{0},\events\right) & = & \emptyset\textrm{ ,}
\end{eqnarray}
\end{subequations}where $\events_{1}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $.
That is, $\bar{\mu}_{0}$ approximates $\proj{\ps}$ if we are only
allowed to use $\events_{0}$ during the measurement, and approximates
$\proj{0}$ if $\events_{1}$ are the only allowed ones. Since $\bar{\mu}_{0}$
approximates different states on different sub-event space, it intuitively
approximates nothing if every projector is allowed.

@@

\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}]\label{thm:Shapley}For
every interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
if the following conditions are true.
\begin{itemize}
\item $\events'$ is commutative, i.e., $\bar{\mu}$ is classical.
\item $\bar{\mu}$ is convex, i.e., for all commuting $P_{0},P_{1}\in\events$,
$\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
\end{itemize}
Then, $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}

@@

Let $\events_{1}$ be the minimal event space containing both $\proj{0}$
and $\proj{\ps}$. Because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
for any mixed state~$\rho\in\coreBorn\left(\bar{\mu},\events_{1}\right)$,
we have $\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$.
Hence, $\rho$ is actually the pure state orthogonal to both $\ket{0}$
and $\ket{\ps}$. The only choice of $\rho$ is $\ket{2}$, and it
is easy to verify $\proj{2}$ is actually in $\coreBorn\left(\bar{\mu},\events_{1}\right)$.

Similarly, let $\events_{2}$ be the minimal event space containing
both $\proj{0}$ and $\proj{\ps'}$. We have $\coreBorn\left(\bar{\mu},\events_{2}\right)=\left\{ \proj{1}\right\} $.
Therefore, 
\begin{equation}
\coreBorn\left(\bar{\mu},\events\right)\subseteq\coreBorn\left(\bar{\mu},\events_{1}\right)\cap\coreBorn\left(\bar{\mu},\events_{2}\right)=\emptyset\textrm{ ,}
\end{equation}
and must be empty.\end{example}
